%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Level 2 - Data \& Analytics Professional} % Job title
    {Globant} % Organization
    {Remote, Colombia} % Location
    {April 2017 - Present} % Date(s)
    {                                                 
      Results-oriented data professional with a track record of leading BI and Data Science projects from conception to implementation. Expert in building and optimizing the data ecosystem to maximize business value.      
      \vspace{1.5em}
      \begin{cvitems}
        \item {Led the design and architecture of Business Intelligence solutions, creating scalable data models and information pipelines that serve as the single source of truth for corporate analysis.}
        \item {Developed and deployed interactive dashboards and executive reports in Power BI, Tableau, etc., enabling senior management to monitor KPIs in real-time.}
        \item {Successfully designed, developed, and optimized complex ETL pipelines using DataStage, dbt, Airflow, and other ETL tools, ensuring data quality and integrity across multiple data sources.}
        \item {Manage, maintain, and optimize databases oriented to data warehouses. (Redshift,DashDB,db2,PostgreSQL)}
        \item {Built and automated scalable data transformation workflows using dbt, airflow on the AWS cloud stack (S3, Redshift), enabling the development of analytical solutions for key business challenges like customer prediction and academic forecasting.}
        \item {Project team management: identifying scope, times and costs in order to meet the objectives of the projects to be executed.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Data BI Engineer} % Job title
    {EY (Ernst \& Young)} % Organization
    {Bogotá, Colombia} % Location
    {July 2014 - April 2017} % Date(s)
    {                                                 
      Proactive BI Developer who initiates and completes impactful BI projects. Strategically designs and improves data infrastructures to elevate business performance and value.
      \vspace{1.5em}
      Implemented and managed comprehensive auditing systems to ensure data integrity, security, and regulatory compliance. Proven ability to establish accountability and enhance operational transparency through meticulous event logging and analysis.      
      \vspace{1.5em}
      \begin{cvitems}
        \item {Led the design and architecture of Business Intelligence solutions, creating scalable data models and information pipelines that serve as the single source of truth for corporate analysis.}
        \item {Developed and deployed interactive dashboards and executive reports in Power BI, Tableau, etc., enabling senior management to monitor KPIs in real-time.}
        \item {Development of OLAP cubes (On-Line Analytical Processing) and ROLAP (Relational On-Line Analytical Processing) Using Microsoft Analytical Suite: SSAS, SSRS and Power BI}
        \item {Successfully designed, developed, and optimized complex ETL pipelines using DataStage, SSIS, and other ETL tools, ensuring data quality and integrity across multiple data sources.}
        \item {Manage, maintain, and optimize databases oriented to data warehouses. (Redshift,DashDB,db2,Redshift,PostgreSQL)}
        \item {Audits of information systems and processes related to IT, applying the methodology EY US Topic-based GAM (Global Audit Methodology).}
      \end{cvitems}
    }
 \cventry
    {Junior to Semi Senior BI Consultant} % Job title
    {Intergrupo - Palmtree - Procalidad} % Organization
    {Bogotá, Colombia} % Location
    {July 2014 - April 2017} % Date(s)
    {                                                 
      As a BI Developer, I advanced from Junior to Semi-Senior level, driving data-driven decision-making through the full lifecycle of business intelligence solutions. My responsibilities encompassed robust data extraction, transformation, and loading (ETL) processes, proficient data warehousing, and comprehensive reporting.
      \vspace{1.5em}
      Through this period, I gained hands-on experience in the entire data ecosystem, from raw data ingestion to delivering polished, business-ready reports, consistently improving data accessibility and reliability for stakeholders.
      \vspace{1.5em}
      \begin{cvitems}
        \item {ETL Tools: Actively designed, developed, and maintained complex ETL pipelines using IBM DataStage, SQL Server Integration Services (SSIS), Oracle Warehouse Builder (OWB) and Kettle. This involved integrating data from disparate sources, ensuring data quality, and optimizing data flow for performance.}
        \item {SQL Databases: Proficiently managed and queried data across various relational database systems including Oracle, SQL Server, MySQL, and Sybase, demonstrating strong SQL scripting and optimization skills.}
        \item {External Sources: Successfully integrated data from a wide array of external sources, including Excel spreadsheets, various flat files, and other proprietary systems, into the data warehouse.}
        \item {Cognos (8.4–10): Developed and delivered impactful reports, dashboards, and analytical solutions using the full suite of Cognos tools, including Framework Manager (for data modeling and package creation), Query Studio, Analysis Studio, and ReportNet.}
        \item {Tableau: Utilized Tableau for creating interactive and visually compelling dashboards, enabling end-users to explore data and derive insights independently.}
        \item {Power BI: Developed and maintained Power BI reports and dashboards, leveraging its advanced visualization capabilities to present complex data in an accessible format for business stakeholders.}
      \end{cvitems}
    }
 
\end{cventries}
